The DAO Hack

### 2019-01-09 paper/paper.tex
added presentation
added another paragraph in conclusion

\subsection{How was that possible?}

@@

The split function contains a function called withdrawRewardFor which calls rewardAccount.payOut which in turn calls \textunderscore recipient.call.value. The first two functions are defined in the DAO code and as an attacker can't change it at will. The call to the recipient, however, is in the attacker's hands and as such, he can do there whatever he desires. This function is used to transfer token to an address by calling a function on that address. In code this looks like that: \cite{deconstructingDaoAttack}

@@

>>>>

@@

The split function contains a function called withdrawRewardFor which calls rewardAccount.payOut which in turn calls \textunderscore recipient.call.value. The first two functions are defined in the DAO code and as such an attacker can't change it at will. The call to the recipient, however, is in the attacker's hands and as such, he can do there whatever he desires. This function is used to transfer token to an address by calling a function on that address. In code this looks like that: \cite{deconstructingDaoAttack}

@@

Today the ethereum network is still influential and hasn't suffered noticeably from this attack or from the decision of the etereum foundation to create a hard fork. New smart contracts certainly benefit from the unique kind of failure of the DAO and can use it as an example of how not to create a smart contract. By learning lessons from this failure newer stronger smart contracts can emerge.
